---
title: "Course Project"
author: "Prerana Chakraborty"
date: "14 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it.In this project, the main goal is to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).\  

## Data Used
The training data for this project are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv \  

## Loading of Data
```{r echo=TRUE}
traindata<-read.csv("traindata.csv")
testdata<-read.csv("testdata.csv")
```

## Cleaning of Data


```{r echo=TRUE,warning=FALSE,message=FALSE}
library(dplyr)
library(ggplot2)
clean <- colSums(is.na(traindata))/nrow(traindata) < 0.95
clntraindata <- traindata[,clean]
clntraindata <- clntraindata[,-c(1:7)]
clean2 <- colSums(is.na(testdata))/nrow(testdata) < 0.95
clntestdata <- testdata[,clean]
clntestdata <- clntestdata[,-c(1:7)]
```
## Data Splitting
```{r echo=TRUE}
library(caret)
library(e1071)
intrain<-createDataPartition(clntraindata$classe,p=0.7,list = FALSE)
traind<-clntraindata[intrain,]
testd<-clntraindata[-intrain,]
```

## ML Algorithm - SVM 
SVM algorithm is applied on the train and test datasets and the accuracy is checked.\   
```{r echo=TRUE} 

model<-svm(classe~.,data=traind)
p<-predict(model,newdata=testd) 
confusionMatrix(p,testd$classe) 
```

## ML Algorithm - Random Forest
Random forest is applied on the train and test datasets and the accuracy is checked.
```{r echo=TRUE}
library(randomForest)
model2<-train(classe~.,method="rf",data=traind,ntree=128)
p2<-predict(model2,newdata=testd)
confusionMatrix(p2,testd$classe)
```
## Prediction
```{r echo=TRUE}
predict(model2,clntestdata)
```
